Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-07-11 template.tex
trying to add the connection between sigma_t and energy

This is the off-cone field equation from \cite{PhysRevD.105.123019}.  The parameter $\sigma_{\rm t}$ is the pulse width, and it depends two quantities: the longitudinal length of the UHE-$\nu$-induced cascade, and the angle at which the cascade is observed relative to the Cherenkov angle.  The parameter $E_0$ is the amplitude normalization, and it depends on two parameters: $\sigma_{\rm t}$, and $\omega_{\rm 0}$, the cutoff frequency from the cascade form factor.

@@

s * r = -\sqrt{\pi}R_0 E_0 \sigma_t^2 \\ \left(xe^{-x^2} \Re\left\lbrace w(q)\right\rbrace + j\frac{1}{2}e^{-x^2} \frac{d\Re\lbrace w(q)\rbrace}{dq} \right) \label{eq:final3}

@@

>>>>

This is the off-cone field equation from \cite{PhysRevD.105.123019}.  The parameter $\sigma_{\rm t}$ is the pulse width, and it depends two quantities: the longitudinal length of the UHE-$\nu$-induced cascade, and the angle at which the cascade is observed relative to the Cherenkov angle.  The parameter $E_0$ is the amplitude normalization, and it depends on two parameters: $\sigma_{\rm t}$, and $\omega_{\rm 0}$, the cutoff frequency from the cascade form factor.  In Sec. \ref{sec:onc}, $E_0$ and $\sigma_t$ will be treated as constants, since neither depends on time.  In Sec. \ref{sec:amp}, the implications of these dependencies will be explored.

@@

s * r = -\sqrt{\pi}R_0 E_0 \sigma_t^2 \\ \left(xe^{-x^2} \Re\left\lbrace w(q)\right\rbrace + \left(\frac{j}{2}\right)e^{-x^2} \frac{d\Re\lbrace w(q)\rbrace}{dq} \right) \label{eq:final3}

@@

\section{The Amplitude of The Signal Model, $s(t)$}
\label{sec:amp}

\begin{itemize}
\item The result for $\mathcal{E}_{r*s}(t)$, Eqs. \ref{eq:final} and \ref{eq:final2}, depends on the model for $s(t)$, Eq. \ref{eq:s}.  The parameters $E_0$ and $\sigma_t$ in Eq. \ref{eq:s} were held constant in Sec. \ref{sec:onc}, because neither depends on time.  The full expression for $s(t)$ was first derived by the authors of \cite{PhysRevD.105.123019}:
\begin{equation}
s(t) = -\frac{E_0\omega_0 \sin(\theta)}{8\pi p}te^{-\frac{t^2}{4p}+p\omega_0^2}\erfc(\sqrt{p}\omega_0) \label{eq:s_full}
\end{equation}
The parameters of Eq. \ref{eq:s_full} are defined in Tab. \ref{tab:param}.
\begin{table*}
\small
\begin{tabular}{| c | c | c | c |} \hline
\textbf{Variable} & \textbf{Definition} & \textbf{Units} & \textbf{Typical Value}\\ \hline
$c$ & speed of light & meter GHz & 0.299792458 \\ 
$\theta_{\rm C}$ & Cherenkov angle & radians & 0.9739 \\ 
$\theta$ & viewing angle from cascade axis & radians & $|\theta-\theta_{\rm C}| = \mathcal{O}(1)$ degree \\ 
$a$ & longitudinal length of cascade (see \cite{10.1103/physrevd.65.016003}) & meter & $\approx 4.2$ at $\approx 10^{16}$ eV \\ 
$n_{max}$ & peak excess charged cascade particles (see \cite{10.1103/physrevd.65.016003})  & none & $\mathcal{O}(10^6)$ at $\approx 10^{16}$ eV \\
$E_{\rm 0}$ & $\propto n_{\rm max}a$ (see \cite{10.1103/physrevd.65.016003}) & V m$^{-1}$ GHz$^{-2}$ & $\approx 1.2$ at $\approx 10^{16}$ eV \\
$p$ & $\frac{1}{2}(a/c)^2 \left(\cos\theta - \cos\theta_C\right)^2$ (see \cite{PhysRevD.105.123019}) & ns$^2$ & depends on $\theta$, $\sqrt{2 p} \approx$ 1 ns \\ 
$\omega_{\rm 0}$ & $\sqrt{\frac{2}{3}} (c\sqrt{2\pi}\rho_{\rm 0})/(n\sin\theta)$ (see \cite{10.1016/j.astropartphys.2017.03.008}) & GHz & depends on $\theta$, $\omega_0/(2\pi)$ is $\mathcal{O}(1)$ GHz \\
$\sqrt{2\pi}\rho_{\rm 0}$ & lateral ICD width (see \cite{10.1016/j.astropartphys.2017.03.008}) & m$^{-1}$ & $\approx 20$ m$^{-1}$ at $\approx 10^{17}$ eV \\
$n$ & index of refraction, ice & none & $1.778 \pm 0.006$ for RF bandwidth \\ \hline
\end{tabular}
\caption{\label{tab:param} things.}
\end{table*}
There is a deep connection between $s(t)$, Eqs. \ref{eq:final}-\ref{eq:final2}, and the natural logarithm of the UHE-$\nu$ cascade energy, $\ln(E_{\rm C}/E_{\rm crit})$. The authors of \cite{PhysRevD.105.123019} have shown that
\begin{equation}
a\Delta\theta = \frac{c \sigma_t}{\sin\theta_{\rm C}}
\end{equation}
\end{itemize}
